---
title: "Installation"
output:
  html_document:
    template: pandoc_template.html
---

## Method 1 (Easy method)

RBMRB version 2.0.2 is available in [CRAN archive](https://CRAN.R-project.org/package=RBMRB) and it can be installed using the following command.
```{r eval=FALSE}
install.packages("RBMRB")
```
This will automatically install all the dependencies. Please make sure all the dependencies are installed corretly otherwise, you will get error messages during runtime. 

## Method 2 (Manual installation from source)

RBMRB library has been developed and tested in R version 3.3.x. It requires the following R packages preinstalled

* httr to import data from BMRB web server(version 1.2.1 or later)
* data.table to format the imported data into a data frame in R (version 1.9.6 or later)
* rjson to deal with BMRB-API (version 0.2.15 or later)
* ggplot2 to simulate spectra (version 2.1.0 or later)
* plotly for interactive graphics in simulated spectra (version 4.5.2 or later)

Please make sure that the correct version of the above packages are already installed.

Here is the instruction to install those packages. Open your R and use the following command
```{r eval=FALSE}
install.packages(c("httr","data.table","rjson","ggplot2","plotly"))
```
Once the necessary packages have been installed, proceed with RMRBM installation. The source file can be downloaded from GitHub

After downloading the source file, use the following command to install RBMRB 

```{r eval=FALSE}
install.packages("~/Downloads/RBMRB_2.0.tar.gz",repos=NULL,type="source")
```
Note: provide the correct path to the downloaded file.

##Method 3 (Development version)

If you have devtools library installed in your R, then you can install the development version directly from GitHub.
```{r eval=FALSE}
library(devtools)
install_github("uwbmrb/RBMRB/RBMRB")
```
