---
title: "Usage"
output:
  html_document:
    template: pandoc_template.html
---


This page explains the general usage of RBMRB package. Detailed documentaion can be found in the help pages of RBMRB package.


```{r}
library(RBMRB)
```

## Data access
BMRB data can be imported in three ways

* **Entry method** Chemical shift data from single or multiple entries
* **Atom method** Chemical shift data from all entries for a given atom
* **Redidue methos** Cehcmial shift data from all entries for a given amio acid/nucleic acid

### Entry method
#### fetch_entry_chemical_shifts:
This function will fetch the ‘Atom_chem_shift’ loop from a NMR-STAR file for a given entry or a list of entries in CSV format. This function works on both macromolecules and metabolites data base. For metabolites entry ids should have right prefix (example ‘bmse000034’)

Example:
```{r}
df1<-fetch_entry_chemical_shifts(15060)
df2<-fetch_entry_chemical_shifts(c(17074,17076,17077))
df2<-fetch_entry_chemical_shifts(c('17074','17076','17077'))
df3<-fetch_entry_chemical_shifts(c('bmse000034','bmse000035','bmse000036'))
```
These data frames have the following columns
```{r}
colnames(df1)
```
Sample data outpu
```{r}
head(df1)
```
### Atom method
fetch_atom_chemical_shifts:
This function will fetch the chemical shift data from all the entries for a given atom. The atom name should be in NMR-STAR atom nomenclature.
Example:
```{r}
df4<-fetch_atom_chemical_shifts('CG2')
df5<-fetch_atom_chemical_shifts('C9')
```
These data frames have the following columns
```{r}
colnames(df4)
```
Sample data outpu
```{r}
head(df4)
```

### Residue method
fetch_res_chemical_shifts:
his function will fetch the chemical shift data from all the entries for a given amino acid (or) nucleic acid. The residue name should be in NMR-STAR  nomenclature. You may optionally specify atom name also

Example:
```{r}
df6<-fetch_res_chemical_shifts('GLY')
df7<-fetch_res_chemical_shifts('HIS','CA')
```
These data frames have the following columns
```{r}
colnames(df6)
```
Sample data output
```{r}
head(df6)
```

## Data manipulation
There are few data manipulation functions are available to rearrange the data frame for easy plottling

### convert_cs_to_n15hsqc:
This function will reformat the chemical shift data frame into a data frame which is easy to plot N15-HSQC spectrum

Example 
```{r}
n15hsqc1<-convert_cs_to_n15hsqc(df1)
n15hsqc2<-convert_cs_to_n15hsqc(df2)
```
The output will look like
```{r}
head(n15hsqc1)
```
This data frame is easy to plot using any plotting library
```{r}
library(ggplot2)
plt1<-ggplot(n15hsqc1)+geom_point(aes(x=H,y=N))
plt1
plt2<-ggplot(n15hsqc2)+geom_point(aes(x=H,y=N,color=Entry_ID))
plt2
plt3<-ggplot(n15hsqc2)+geom_point(aes(x=H,y=N,color=Entry_ID))+geom_line(aes(x=H,y=N,group=Comp_index_ID))
plt3
```

### convert_cs_to_c13hsqc:
This function will reformat the chemical shift data frame into a data frame which is easy to plot C13-HSQC spectrum

Example 
```{r}
c13hsqc1<-convert_cs_to_c13hsqc(df1)
c13hsqc2<-convert_cs_to_c13hsqc(df2)
```
The output will look like
```{r}
head(c13hsqc1)
```
This data frame is easy to plot using any plotting library
```{r}
library(ggplot2)
plt1<-ggplot(c13hsqc1)+geom_point(aes(x=H,y=C))
plt1
plt2<-ggplot(c13hsqc2)+geom_point(aes(x=H,y=C,color=Entry_ID))
plt2
plt3<-ggplot(c13hsqc2)+geom_point(aes(x=H,y=C,color=Entry_ID))+geom_line(aes(x=H,y=C,group=Comp_index_ID))
plt3
```

### convert_cs_to_tocsy:
This function will reformat the chemical shift data frame into a data frame which is easy to plot the TOCSY spectrum from the data. Note : Since both dimensions have proton chemical shifts, the columns are named as Val.x and Val.y

Example
```{r}
tocsy1<-convert_cs_to_tocsy(df1)
tocsy2<-convert_cs_to_tocsy(df2)
```
after conversion the data will look like
```{r}
head(tocsy1)
```

plotting TOCSY spectrum
```{r}
library(ggplot2)
plt1<-ggplot(tocsy1)+geom_point(aes(x=Val.x,y=Val.y))
plt1
plt2<-ggplot(tocsy2)+geom_point(aes(x=Val.x,y=Val.y,color=Entry_ID))
plt2
```

### filter_residue:
This function will filter the data frame and remove all non standard amino acids. The data frame should contain the amino acid information in the Comp_ID column

Example
```{r}
df6<-fetch_atom_chemical_shifts('CG2')
df7<-filter_residue(df6)
```
after filtering the data frame contains data only from standard 20 amino acids
