---
title: "Usage"
output:
  html_document:
    template: pandoc_template.html
---


This page explains the general usage of RBMRB package. Detailed documentaion can be found in the help pages of RBMRB package.


```{r}
library(RBMRB)
```

## Data access
BMRB data can be imported in three ways

* **Entry method** Chemical shift data from single or multiple entries
* **Atom method** Chemical shift data of a particular atom
* **Redidue methos** Cehcmial shift data of an amio acid/nucleic acid
* **Local data** User data in NMR-STAR format (Not available or deposited in BMRB)

### Entry method
#### fetch_entry_chemical_shifts:
This function will fetch the ‘Atom_chem_shift’ loop from a NMR-STAR file for a given entry or a list of entries. This function works on both macromolecules and metabolites data base. For metabolites entry id should have right prefix (example ‘bmse000034’)

Example:
```{r}
df1<-fetch_entry_chemical_shifts(15060)
df2<-fetch_entry_chemical_shifts(c(17074,17076,17077))
df2<-fetch_entry_chemical_shifts(c('17074','17076','17077'))
df3<-fetch_entry_chemical_shifts(c('bmse000034','bmse000035','bmse000036'))
```
These data frames have the following columns
```{r}
colnames(df1)
```
Sample data output
```{r}
head(df1)
```
### Atom method
####fetch_atom_chemical_shifts:
This function will fetch the chemical shift data from all the entries for a given atom. The atom name should be in NMR-STAR atom nomenclature.
Example:
```{r}
df4<-fetch_atom_chemical_shifts('CG2')
df5<-fetch_atom_chemical_shifts('C9')
```
These data frames have the following columns
```{r}
colnames(df4)
```
Sample data output
```{r}
head(df4)
```

### Residue method
####fetch_res_chemical_shifts:
This function will fetch the chemical shift data from all the entries for a given amino acid (or) nucleic acid. The residue name should be in NMR-STAR  nomenclature. You may optionally specify atom name as a parameter

Example:
```{r}
df6<-fetch_res_chemical_shifts('GLY')
df7<-fetch_res_chemical_shifts('HIS','CA')
```
These data frames have the following columns
```{r}
colnames(df6)
```
Sample data output
```{r}
head(df6)
```

### Local data
User may also have the posibility of visualizing their own data using RBMRB tools. They can upload their data into BMRB API server and visualize the data. The data will be stored for seven datas and the user will get unique token to access the data, which can be used insted of BMRB ID. This allows the user to share his data visualization anywhere around the world. 

#### Upload NMR-STAR file 
```{r eval=FALSE}
token<-export_star_data('hpr_chem_shift.str')
```

#### To visualize the data
```{r eval=FALSE}
hsqc_spec<-HSQC_15N(token)
```


## Data manipulation
There are few data manipulation functions available to rearrange the data frame for easy visualization

### convert_cs_to_n15hsqc:
This function will reformat the chemical shift data frame into a simple dataframe that contains algorithmically combined proton and nitrogen chemical shifts in two columns
Example 
```{r}
n15hsqc1<-convert_cs_to_n15hsqc(df1)
n15hsqc2<-convert_cs_to_n15hsqc(df2)
```
The output will look like
```{r}
head(n15hsqc1)
```
This data frame is easy to plot using any plotting library
```{r}
library(ggplot2)
plt1<-ggplot(n15hsqc1)+geom_point(aes(x=H,y=N))
plt1
plt2<-ggplot(n15hsqc2)+geom_point(aes(x=H,y=N,color=Entry_ID))
plt2
plt3<-ggplot(n15hsqc2)+geom_point(aes(x=H,y=N,color=Entry_ID))+geom_line(aes(x=H,y=N,group=Comp_index_ID))
plt3
```

### convert_cs_to_c13hsqc:
This function will reformat the chemical shift data frame into a simple dataframe that contains proton and carbon chemical shifts in two columns

Example 
```{r}
c13hsqc1<-convert_cs_to_c13hsqc(df1)
c13hsqc2<-convert_cs_to_c13hsqc(df2)
```
The output will look like
```{r}
head(c13hsqc1)
```
This data frame is easy to plot using any plotting library
```{r}
library(ggplot2)
plt1<-ggplot(c13hsqc1)+geom_point(aes(x=H,y=C))
plt1
plt2<-ggplot(c13hsqc2)+geom_point(aes(x=H,y=C,color=Entry_ID))
plt2
plt3<-ggplot(c13hsqc2)+geom_point(aes(x=H,y=C,color=Entry_ID))+geom_line(aes(x=H,y=C,group=Comp_index_ID))
plt3
```

### convert_cs_to_tocsy:
This function will reformat the chemical shift data frame into a simple dataframe that contains algorithmically combined proton shifts in two columns. Note : Since both dimensions have proton chemical shifts, the columns are named as Val.x and Val.y

Example
```{r}
tocsy1<-convert_cs_to_tocsy(df1)
tocsy2<-convert_cs_to_tocsy(df2)
```
after conversion the data will look like
```{r}
head(tocsy1)
```

plotting TOCSY spectrum
```{r}
library(ggplot2)
plt1<-ggplot(tocsy1)+geom_point(aes(x=Val.x,y=Val.y))
plt1
plt2<-ggplot(tocsy2)+geom_point(aes(x=Val.x,y=Val.y,color=Entry_ID))
plt2
```

### filter_residue:
This function will filter the data frame and remove all non standard amino acids. The data frame should contain the amino acid information in the Comp_ID column

Example
```{r}
df6<-fetch_atom_chemical_shifts('CG2')
df7<-filter_residue(df6)
```
after filtering the data frame contains data only from standard 20 amino acids
